%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

%%%%%%%%Two options for having a bibliography. If you use a separate file or multiple files:
%\bibliography{./robotics,./imageprocessing,./thesis}
%%%%% where the files are robotics.bib, imageprocessing.bib and/or thesis.bib. 

%Or you can include the bibliography entries directly:

\begin{thebibliography}{99}

\bibitem{hahn} Jane Hahn, ``\LaTeX{} For Everyone,'' Personal TeX Inc., 
  12 Madrona Street, Mill Valley, California.

\bibitem{goossens} Frank Mittelbach and Michel Goossens (with
Johannes Braams, David Carlisle, and Chris Rowley),
  ``The \LaTeX{} Companion,'' second edition, Addison-Wesley, 2004.

\bibitem{GRM:LaTeXGraphicsCompanion} 
Michal Goossens, Sabastian Rahtz, and Frank Mittelbach, ``The \LaTeX{} 
Graphics Companion,'' Addison-Wesley, 1997.

\bibitem{Gra:MathIntoLaTeX} George Gr\"atzer, ``Math into \LaTeX: An 
introduction to \LaTeX{} and \mbox{\AmS-\LaTeX},'' Birkh\"auser, 1996.

\bibitem{hoenig} Alan Hoenig, ``\TeX{} Unbound: \LaTeX{} and \TeX{} strategies
for Fonts, Graphics, and More,'' Oxford University Press, 1997. Includes
practical advice and numerous exammples for a wide range of topics,
includeing virtual fonts, graphics, and resources for the internet and
multimedia.

\bibitem{KH} Helmut Kopka and Patrick W. Daly, ``A Guide to \LaTeXe:
  Document Preparation for Beginners and Advanced Users,'' 2nd ed.,
  Addison-Wesley, 1995.

\bibitem{lamport} Leslie Lamport, ``\LaTeX: A Document Preparation
  System,'' 2nd ed., Addison-Wesley, 1994.

\bibitem{walsh} Norman Walsh, ``Making \TeX{} Work,'' O'Reilly and
  Associates, 1994.

\end{thebibliography}

