%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\chapter{Gruenhage's Locally Finite Games}

A variation of $\gruConGame{X}{x}$, also due to Gruenhage,
may be used to characterize various covering properties, particularly
for locally compact spaces. All spaces are assumed to be $T_1$ in this
chapter.

\section{Characterizations using $\gruKPGame{X}$, $\gruKLGame{X}$}

\begin{game}
  Let $\gruKPGame{X}$ denote the \term{Gruenhage compact/point game}
  with players $\pl K$, $\pl P$. During round $n$, $\pl K$ chooses
  a compact subset $K_n$ of $X$, followed by $\pl P$ choosing a point
  $p_n\in X$ such that $p_n\not\in \bigcup_{m\leq n}K_m$.

  $\pl K$ wins the game if the collection $\{\{p_n\}:n<\omega\}$ is locally
  finite in the space, and $\pl P$ wins otherwise.
\end{game}

This game is often formulated by requiring that the collection
$\{\{p_n\}:n<\omega\}$ be discrete. With the knowledge of at least the latest
move of the opponent, $\pl K$ may guarantee that if $\{\{p_n\}:n<\omega\}$
is locally finite then it is also discrete, since she may require
$p_n\in K_{n+1}$. Thus this formulation is essentially equivalent to the usual
formulation for all existing applications.

We may relate this game to $\gruConGame{X}{x}$ as follows:

\begin{thm}
  If $X$ is locally compact, then for $k<2$:
    \begin{itemize}
      \item $\pl K\win\gruKPGame{X}$ if and only if
        $\pl O\win\gruConGame{\oneptcomp{X}}{\infty}$.
      \item $\pl K\kmarkwin{k}\gruKPGame{X}$ if and only if
        $\pl O\kmarkwin{k}\gruConGame{\oneptcomp{X}}{\infty}$.
      \item $\pl K\ktactwin{k}\gruKPGame{X}$ if and only if
        $\pl O\ktactwin{k}\gruConGame{\oneptcomp{X}}{\infty}$.
    \end{itemize}
\end{thm}

\begin{proof}
  Let $L$ be any of $\nu_0$, $\nu_1$, $\mu_0$, $\mu_1$, or the identity.
  For any sequence $s$ of points in $\oneptcomp X$, let $s'$ be the
  subsequence of non-$\infty$ points in $s$.

  If $\sigma\circ L$ is a winning strategy for $\pl K$ in $\gruKPGame{X}$, let
  $\tau\circ L$ be a strategy for $\pl O$ in $\gruConGame{\oneptcomp X}{\infty}$
  such that $\tau(L(s)) = \oneptcomp X\setminus \sigma(L(s)')$. Then for
  any legal attack $p$ against $\tau$, $p'$ is a legal attack against $\sigma$.
  (The proof of this claim uses the fact that $k<2$.)
  If $p'$ is a finite sequence, then $p$ converges to $\infty$.
  Otherwise, the set $\{\{p'(n)\}:n<\omega\}$ is locally finite in $X$, so
  $\{p'(n):n<\omega\}$ is a closed discrete subset of $X$. Then for every
  neighborhood $U$ of $\infty$, $X\setminus U$ is contained in a compact set,
  so it cannot contain a closed discrete subset. Thus $p'$ and $p$
  converge to $\infty$.

  If $\sigma\circ L$ is a winning strategy for $\pl O$ in
  $\gruConGame{\oneptcomp X}{\infty}$, let $\tau\circ L$ be a strategy for
  $\pl K$ in $\gruKPGame{X}$ such that $\tau(L(s))= X\setminus\sigma(L(s))$.
  Then for any legal attack $p$ against $\tau$, $p$ is a legal attack against
  $\sigma$, so the sequence $p$ converges to $\infty$. For any point $x\in X$
  distinct from the $p(n)$, we may choose a neighborhood $U_x$ of $x$ in $X$
  missing every point in $p(n)$.
  For every $n<\omega$, we may choose a neighborhood $U_{p(n)}$ of $p(n)$ in
  $X$ which misses every distinct $p(m)$. Thus $\{\{p(n)\}:n<\omega\}$ is a
  locally finite collection.
\end{proof}

The reason why $\gruConGame{\oneptcomp X}{\infty}$ and $\gruKPGame{X}$ are
not completely equivalent is due to the fact that $\pl P$ may hide information
from $\pl O$ by playing $\infty$. These moves cannot trivially be ignored
using a $k$-limited information strategy for $k\geq 2$, since $\pl P$ may
ensure that only one ``useful'' move may be seen by $\pl K$ at a time by playing
$k$ $\infty$'s between each non-$\infty$.

Applications of limited information strategies for $\pl K$ are already known;
see \cite{MR858337}.

\begin{defn}
  A space is \term{metacompact} if for every open cover $\mc U$ there exists a
  point-finite open refinement $\mc V$ of $\mc U$ also covering the space.
\end{defn}

\begin{thm}
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is metacompact
      \item $\pl K \tactwin \gruKPGame{X}$.
    \end{itemize}
\end{thm}

\begin{defn}
  A space is \term{$\sigma$-metacompact} if for every open cover $\mc U$ there
  exist point-finite open refinements $\mc V_n$ of $\mc U$ such that
  $\bigcup_{n<\omega}\mc V_n$ also covers the space.
\end{defn}

\begin{thm}
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is $\sigma$-metacompact
      \item $\pl K \markwin \gruKPGame{X}$.
    \end{itemize}
\end{thm}

In addition, it's trivial to show the following.

\begin{prop}
  The following are equivalent for any space $X$:
    \begin{itemize}
      \item $X$ is compact
      \item $\pl K \ktactwin{0} \gruKPGame{X}$.
    \end{itemize}
\end{prop}

\begin{proof}
  A $0$-tactic is seeded with zero information about the moves of the opponent
  or the round number, so it must be a constant function valued at $X$.
\end{proof}

A similar game may be considered by allowing the second player to choose
compact sets rather than points, which provided in \cite{MR858337}
a game-theoretic characterization of paracompactness for locally compact
spaces.

\begin{game}
  Let $\gruKLGame{X}$ denote the \term{Gruenhage compact/compact game}
  with players $\pl K$, $\pl L$. This game proceeds analogously to
  $\gruKPGame{X}$, except the second player $\pl L$ chooses compact sets $L_n$
  missing $\bigcup_{m\leq n}K_n$,
  and $\pl K$ wins if the collection $\{L_n:n<\omega\}$ is locally finite.
\end{game}

As above, this formulation is equivalent to requiring $\{L_n:n<\omega\}$ be
discrete when considering strategies for $\pl K$ which use at least the latest
move of $\pl L$.

\begin{defn}
  A space is \term{paracompact} if for every open cover $\mc U$ there exists a
  locally-finite open refinement $\mc V$ of $\mc U$ also covering the space.
\end{defn}

\begin{thm}
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is paracompact
      \item $\pl K \win \gruKLGame{X}$.
    \end{itemize}
\end{thm}


\section{Locally compact spaces and predetermined strategies}

As mentioned above, adding knowledge of the round number to a tactic changes the
characterization from metacompact to $\sigma$-metacompact. In fact, the
analogous result holds
for $0$-tactics to $0$-marks, known as predetermined strategies since they
rely only on the round number and not the moves of the opponent.

\begin{thm}
  If $X$ is a locally compact Lindel\"of space, then $\pl K \prewin G_{K,L}(X)$.
\end{thm}

\begin{proof}
  For each $x\in X$, let $U_x$ be an open neighborhood of $x$ with $\cl{U_x}$
  compact. Then as $X$ is Lindel\"of, choose $x_n\in X$ for $n<\omega$ such that
  $\{U_{x_n}:n<\omega\}$ covers $X$. Define the predetermined strategy $\sigma$
  for $\pl K$ by $\sigma(n)=\cl{U_{x_n}}$.

  Let $L:\omega\to \mc K(X)$ legally attack $\sigma$, so
  $L(n)\cap\bigcup_{m\leq n}\sigma(m)=\emptyset$. For each $x\in X$,
  choose $n<\omega$ with $x\in U_{x_n}$. Then $U_{x_n}$ is a neighborhood of
  $x$ which intersects finitely many $L(n)$, so $\{L(n):n<\omega\}$ is
  locally finite.
\end{proof}

\begin{defn}
  A space $X$ is \term{hemicompact} if there exist compact sets $K_n$ for
  $n<\omega$ such that every compact set in $X$ is a subset of some $K_n$.
\end{defn}

\begin{thm}
  If $\pl K\prewin \gruKPGame{X}$, then $X$ is hemicompact.
\end{thm}

\begin{proof}
  Let $\sigma$ be a winning predetermined strategy for $\pl K$ in
  $\gruKPGame{X}$. If $C\in \mc K(X)$ is compact, then for each $x\in C$ let
  $U_x$ be an open neighborhood of $x$ which intersects finitely many
  $\sigma(n)$. Choose $x_i\in C$ for $i<n<\omega$ such that
  $\{U_{x_i}:i<n\}$ covers $C$. Then $\bigcup_{i<n}U_{x_i}$ contains $C$
  and intersects finitely many $\sigma(n)$, and thus
  $\{\bigcup_{m\leq n}\sigma(m):n<\omega\}$ witnesses hemicompactness.
\end{proof}

\begin{cor}
  The following are equivalent for any locally compact space $X$:
    \begin{itemize}
      \item $X$ is Lindel\"of.
      \item $X$ is $\sigma$-compact.
      \item $X$ is hemicompact.
      \item $\pl K \prewin \gruKPGame{X}$.
      \item $\pl K \prewin \gruKLGame{X}$.
    \end{itemize}
\end{cor}

\section{Compactly generated spaces and predetermined strategies}

\begin{defn}
  A space $X$ is \term{compactly generated} if a set is closed if and
  only if its intersection with every compact set is closed. Such
  spaces are also known as \term{$k$-spaces}.
\end{defn}

All locally compact spaces are $k$-spaces. As will be shown,
the games $\gruKPGame{X}$, $\gruKLGame{X}$ are equivalent for $\pl K$'s
predetermined strategies in Hausdorff $k$-spaces.

\begin{defn}
  A space $X$ is a $k_\omega$-space if there exist compact sets $K_n$ for
  $n<\omega$ such that a set is closed if and
  only if its intersection with every $K_n$ is closed.
\end{defn}

\begin{thm}
  If $X$ is a $k_\omega$-space, then
  $\pl K \prewin \gruKLGame{X}$.
\end{thm}

\begin{proof}
  Let $K_n$ witness that $X$ is a $k_\omega$-space. Define the predetermined
  strategy $\sigma$ for $\pl K$ by $\sigma(n)=K_n$.

  Let $L:\omega\to\mc{K}(X)$ be a legal attack against $\sigma$, and let
  $L_{\omega\setminus n} = \bigcup_{n\leq m<\omega}L(m)$. Then as
    \[
      L_{\omega\setminus n}\cap K_p
        =
      \bigcup_{n\leq m< p}L(m) \cap \sigma(p)
    \]
  is compact for each $p<\omega$, $L_{\omega\setminus n}$ is closed.

  For each $x\in X$, $x\in \sigma(p)$ for some $p$, so
  $x\in X\setminus L_{\omega\setminus p}$ which misses all but finitely
  many $L(n)$, showing that $\{L(n):n<\omega\}$ is locally finite and
  $\sigma$ is a winning predetermined strategy.
\end{proof}

The following result was observed in \cite{MR540599}; a proof is provided
for convenience.

\begin{prop}
  Hemicompact $k$-spaces are $k_\omega$-spaces.
\end{prop}

\begin{proof}
  Let $K_n$ for $n<\omega$ witness hemicompactness.
  If $C\cap K_n$ is closed for each $n<\omega$, then let $K$ be any compact
  set. Since $K\subseteq K_n$ for some $n<\omega$, $C\cap K$ is closed, and
  therefore $C$ is closed.
\end{proof}

As we've already seen that $\pl K \prewin \gruKPGame{X}$ implies
hemicompactness:

\begin{cor}
  The following are equivalent for any $k$-space $X$:
    \begin{itemize}
      \item $X$ is $k_{\omega}$.
      \item $X$ is hemicompact.
      \item $\pl K \prewin \gruKPGame{X}$.
      \item $\pl K \prewin \gruKLGame{X}$.
    \end{itemize}
\end{cor}

\section{Non-equivalence of $\gruKPGame{X}$, $\gruKLGame{X}$}

For $k$-spaces, it has been shown that $\gruKPGame{X}$ and $\gruKLGame{X}$
are equivalent with respect to $\pl K$'s winning predetermined strategies.
Looking at a subspace of the Stone-Cech compactification $\beta\omega$ of
$\omega$ reveals an example for which the predetermined strategies are not
equivalent.

\begin{defn}
  An \term{ultrafilter} on a cardinal $\kappa$ is a maximal filter of non-empty
  subsets of $\kappa$. For each $\alpha\in \kappa$, the ultrafilter
  $\mc F_\alpha$ containing all supersets of $\{\alpha\}$ is called a
  \term{principal ultrafilter}. All
  ultrafilters not of this form are called \term{free ultrafilters}.
\end{defn}

\begin{defn}
  The \term{Stone-Cech compactification} of a cardinal
  $\kappa$ is the space $\beta\kappa$ consisting
  of all ultrafilters on $\kappa$, with open sets of the form
  $U_S=\{\mc F\in\beta\kappa : S\in\mc F\}$ for $S\subseteq \kappa$.
\end{defn}

From these definitions it is easily verified that principal ultrafilters
are isolated, so $\kappa$ with the discrete topology may be viewed as
a dense open subspace of $\beta\kappa$. $\beta\kappa$ is also compact, so
$\pl K\ktactwin{0}\gruKLGame{\beta\kappa}$; of greater interest is the subspace
of $\beta\omega$ consisting of all principal ultrafilters and a single free
ultrafilter $\mc F$, denoted $\omega\cup\{\mc F\}$.

\begin{lem}
  All compact subsets of $\omega\cup\{\mc F\}\subset\beta\omega$ are finite.
  In particular, the difference of compact sets in $\omega\cup\{\mc F\}$
  is compact.
\end{lem}

\begin{proof}
  Let $I=\{n_i:i<\omega\}\cup\{\mc F\}$ be infinite.
  Then $\{U_{\omega\setminus\{n_i:i\geq j\}}:j<\omega\}$ is an open cover of
  $I\cup\{\mc F\}$ with no finite subcover.
\end{proof}

\begin{thm}
  $\pl K\notprewin \gruKLGame{\omega\cup\{\mc F\}}$ for any free
  ultrafilter $\mc F$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a predetermined strategy for $\pl K$, and define the legal
  counter-attack $H:\omega\to\mc K(X)$ by
  $H(n)=(n\cup\sigma(n+1))\setminus\sigma(n)$. Then for any neighborhood
  $U_S$ of $\mc F$, $S$ is infinite, and since
  $\bigcup_{n<\omega} H(n)\supseteq\omega\setminus\sigma(0)$, $U_S$ meets
  infinitely many of the finite $H(n)$. Thus $\sigma$ is not a winning
  predetermined strategy.
\end{proof}

\begin{thm}
  There exists a free ultrafilter $\mc F$ such that
  $\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$.
\end{thm}

\begin{proof}
  Let $\mc F$ be any free ultrafilter, and
  define the predetermined strategy $\sigma$ by
  $\sigma(n)=n^2\cup\{\mc F\}$.

  Consider the set of all legal attacks $A\subseteq\omega^\omega$ by
  $\pl P$ against $\sigma$. For $\{f_i:i\leq m\}\in [A]^{<\omega}$ and
  $m<n<\omega$, each $f_i$ maps only $n$ points into $n^2$, so
  $\bigcup_{i\leq m}\ran{f_i}$ is coinfinite.
  Then $\mc G'=\{\omega\setminus\ran f : f\in A\}$ is contained in a free
  ultrafilter $\mc G$, and if $\mc F=\mc G$, then $\sigma$ is a
  winning predetermined strategy.
\end{proof}

It is not possible to prove in $ZFC$ that
$\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$
for arbitrary free ultrafilters.

\begin{defn}
  A \term{selective ultrafilter} $\mc S$ is a free ultrafilter with the
  property that for every
  partition $\{B_n : n < \omega\}$ of nonempty subsets of $\omega$ such that
  $B_n \not\in \mc{S}$ for all $n$, there exists $A \in \mc{S}$ such
  that $|A \cap B_n|=1$ for all $n$.
\end{defn}

\begin{thm}
  CH implies the existence of a selective ultrafilter.
  \cite{MR0080902}
\end{thm}

\begin{thm}
  If $\mc S$ is a selective ultrafilter, then
  $\pl K\notprewin \gruKPGame{\omega\cup\{\mc S\}}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a predetermined strategy for $\pl K$ such that
  $\sigma(n)\supset\bigcup_{m<n}\sigma(m)$.
  Then define $B_n=\omega\cap(\sigma(n+1)\setminus\sigma(n))$. Since $B_n$
  is always nonempty finite, $B_n\not\in\mc F$ and there exists $A\in \mc S$
  such that $|A\cap B_n|=1$.

  Define the legal counter-attack $p:\omega\to\omega\cup\{\mc S\}$ by
  $p(n)\in A\cap B_n=A\cap(\sigma(n+1)\setminus\sigma(n))$. Since
  $A=(A\cap\sigma(0))\cup\{p(n):n<\omega\}$, $\{p(n):n<\omega\}\in\mc S$.
  Therefore, every neighborhood of $\mc F$ intersects infinitely many of
  the $p(n)$, and $p$ defeats the predetermined strategy $\sigma$.
\end{proof}

Of particular note is that the author knows of no examples of a
non-$k$-space such that $K\prewin\gruKPGame{X}$.

\begin{ques}
  Does $K\prewin\gruKPGame{X}$ imply $X$ is a $k$-space?
\end{ques}


\section{Tactics and marks for $\gruKPGame{X}$}

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a locally-compact space $\pmb X$ for which
$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\notkmarkwin{k}\gruKPGame{\pmb X}$
for any $k<\omega$.

\begin{defn}
  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct
  clopen sets, along with an uncountable subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\pmb X$ is given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $B_{\alpha,m}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
  $m<\omega$.
\end{defn}

\begin{defn}
  Let $F\in \omega_1^{<\omega}$ and $m,n<\omega$.
  \[
    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
  \]
  \[
    a_n = \{\<i,0\>:i<n\}\cup\{\<n,1\>\}
  \]
  \[
    A = \{a_n : n<\omega\}
  \]
  \[
    K_F' = K_F \setminus (X \times A)
  \]
  \[
    L_m = X \times 2^{<m}
  \]
\end{defn}

\begin{lem}
  $K_F$, $K_F'$, and $L_m$ are compact in $\pmb X$.
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lem}

\begin{proof}
  $K_F$ contains $C_F=\{c_\alpha: \alpha\in F\}\subseteq C$, so any
  cover of basic open sets must include $B_{\alpha,n_\alpha}$ for each
  $\alpha\in F$, and the remaining uncovered portion of $K_F$ is a closed
  subset of a finite union of copies of compact $X$. Then $K_F'$ is also
  compact as it is a closed subset of $K_F$, and $L_m$ is compact as it
  is a finite union of copies of compact $X$.

  Let $D$ be compact. Consider the open cover
    \[
      \{
        B_{\alpha,0}
      :
        \alpha<\omega_1
      \}
      \cup
      \{
        X\times\{s\}
      :
        s\in 2^{<\omega}
      \}
    \]
  and note that the finite subcover for $D$ contains subsets of some
  $K_F' \cup L_m$.
\end{proof}

\begin{thm}
  $\pl K\win\gruKPGame{\pmb X}$.
\end{thm}

\begin{proof}
  Since $\{U_\alpha:\alpha<\omega_1\}$ is a point-countable cover,
  for each $x\in X$ let $\alpha_{x,n}<\omega_1$ yield
  ordinals such that $x\in U_{\alpha_{x,n}}$ for $n<\omega$.

  Let $M:\pmb X\times \omega\to \mc K(\pmb X)$ as follows:
    \[
      M(\pmb x,n)
        =
      \left\{
        \begin{array}{lcl}
          K_{\{\alpha_{x,m}:m\leq n\}}
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          K_{\{\alpha\}}
        & : &
          \pmb x = c_\alpha \in C
        \end{array}
      \right.
    \]
  and use $M$ to define the strategy $\sigma$ for each $\pmb a\in\pmb X^{<\omega}$:
    \[
      \sigma(\pmb a)
        =
      L_{|\pmb a|}
        \cup
      \bigcup_{i< |\pmb a|}
      M(\pmb a(i),|\pmb a|)
    \]

  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\sigma$. Then as
  $\pmb p(n)\not\in L_n$, for each $\pmb x=\<x,s\>\in X\times 2^{<\omega}$,
  $X\times\{s\}$ is an open neighborhood of $\pmb x$ which contains finitely
  many $\pmb p(n)$.

  Now consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
  Then if $\pmb p(n)=\<x,s\>$ with $\alpha = \alpha_{x,N}$ for some $N<\omega$,
  then $\pmb p(m)\not\in B_{\alpha,0}$ for $\max(n,N)<m<\omega$.
  Or, if $\pmb p(n)=c_\alpha$, then
  $\pmb p(m)\not\in B_{\alpha,0}$ for $n<m<\omega$.
  Otherwise, $\pmb p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
  In any case, $B_{\alpha,0}$ is a neighborhood of $\pmb x$ which contains finitely
  many $\pmb p(n)$. Therefore, $\sigma$ is a winning strategy.
\end{proof}

We will show that there does not exist any winning $k$-Markov strategy for
$\pl K$ in this game. Knowledge of round number does not assist $\pl K$,
since she may force $\pl P$ to either stay within $C$, or to seed a growing
integer by forcing her to play outside $L_{|s|+1}$ in response to
$\<x,s\>\in X\times 2^{<\omega}$.

\begin{lem}
  If $\pl K\kmarkwin{k+1}\gruKPGame{\pmb X}$, then
  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  Let $\sigma$ be a winning $(k+1)$-mark for $\pl K$ such that $m\leq n$ and
  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  For a sequence $p$, let $p\rest^k n=\nu_k(p\rest n)$ give the last $k$
  terms of $p\rest n$.

  Define $r:\pmb X\to\omega$ by
    \[
      r(\pmb x)
        =
      \left\{
        \begin{array}{lcl}
          |s|
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          0
        & : &
          \pmb x \in C
        \end{array}
      \right.
    \]
  and use $r$ to define the $(k+1)$-tactic $\tau$ by
    \[
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]
    \[
      \tau(\pmb t\concat\<\pmb x\>)
        =
      L_{r(\pmb x)+1}
        \cup
      \{\pmb x\}
        \cup
      \sigma(\pmb t\concat\<\pmb x\>,r(\pmb x)+1)
    \]

  Let $\pmb p:\omega\to\pmb X$ be a legal attack by $\pl P$ against $\tau$.
  If $\pmb p(n)\in C$ for $N<n<\omega$, then since no $\pmb p(n)$ may be legally
  repeated, $\{\{\pmb p(n)\}:N<n<\omega\}$ is a discrete collection, making
  $\{\{\pmb p(n)\}:n<\omega\}$ locally finite.

  Otherwise, let $f\in\omega^\omega$ be increasing and define
  $\pmb q:\omega\to X\times 2^{<\omega}$ such that $\pmb q(i)=\pmb p(f(i))$,
  and $\pmb p(j)\in X\times 2^{<\omega}$ implies there is some $i$ with $j=f(i)$.
  It follows that
    \[
      \pmb q(0)
        =
      \pmb p(f(0))
        \not\in
      \bigcup_{m\leq f(0)}\tau(\pmb p \rest^{k+1} m)
        \supseteq
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]

  Denoting $\pmb q(n)=\<x_n,s_n\>$, it's trivial to note that $|s_0|\geq 0$.
  Assuming that $|s_m|\geq m$ for $m\leq n$,
  it then follows that
    \[
      \pmb q(n+1)
        =
      \pmb p(f(n+1))
        \not\in
      \bigcup_{m\leq f(n+1)}\tau(\pmb p\rest^{k+1} m)
    \]
    \[
        \supseteq
      \bigcup_{m\leq n}\tau(\pmb q\rest^{k+1} m)
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),|s_m|+1)
    \]
    \[
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),m+1)
    \]
  and
    \[
      \pmb q(n+1)
        \not\in
      \tau(\pmb q\rest^{k+1} (n+1))
        \supseteq
      L_{r(\pmb q(n))}
        =
      L_{|s_n|+1}
    \]
  gives $|s_{n+1}|\geq|s_n|+1\geq n+1$.
  Thus $\pmb q$ is a legal attack on the winning $(k+1)$-Markov strategy
  $\sigma$, so the collection $\{\{\pmb q(n)\}:n<\omega\}$ is locally finite.
  and it follows that $\{\{\pmb p(n)\}:n<\omega\}$ is also locally finite.
\end{proof}

\begin{cor}
  $\pmb X$ is $\sigma$-metacompact if and only if $\pmb X$ is metacompact.
\end{cor}

\begin{lem}
  If $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$, then
  $\pl K\tactwin\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  Let $\sigma$ be a winning $(k+1)$-tactical strategy, and without loss of
  generality assume it ignores order.

  Define $F(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ and
  $m(x_0,\dots,x_{k},n)\in\omega\setminus(n+1)$, both increasing on $n$,
  such that for each $\<x_0,\dots,x_{k}\>\in X^{k+1}$,
  \[
    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}}
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
      \subseteq
    K'_{F(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
  \]

  Select an arbitrary point $y \in X$.
  Let
    \[
      M^0(x,n)=n
    \]
    \[
      M^{i+1}(x,n)=m(x,y,\dots,y,M^i(x,n)+1)
    \]
  and define the tactical strategy $\tau$ as follows:
  \[
    \tau(\emptyset)
      =
    \sigma(\emptyset)
  \]
  \[
    \tau(\<c_\alpha\>)
      =
    \{c_\alpha\}
  \]
  \[
    \tau(\<\<x,s\>\>)
      =
    K'_{F(x,y,\dots,y,M^k(x,|s|)+1)}
      \cup
    L_{m(x,y,\dots,y,M^k(x,|s|)+1)}
  \]

  Let $\pmb p:\omega\to \pmb X$ be a legal attack against
  $\tau$, and assume $\pmb p(n)=\<x_n,s_n\>\in X\times 2^{<\omega}$.
  Then consider the attack $\pmb q:\omega\to X\times 2^{<\omega}$ against
  $\sigma$ defined by, for $n<\omega$ and $i<k$,
    \[
      \pmb q((k+1)n)=\pmb p(n)=\<x_n,s_n\>
    \]
    \[
      \pmb q((k+1)n+(i+1))=\<y, a_{M^{i+1}(x_n,|s_n|)}\>
    \]

  Since
    \[
      \<x_{n+1},s_{n+1}\>
        =
      \pmb p(n+1)
        \not\in
      \tau(\<\pmb p(n)\>)
        \supseteq
      L_{M^{k+1}(x_n,|s_n|)+1}
    \]
  it follows that
  $|s_{n+1}|\geq M^{i+1}(x_n,|s_n|)+1$ for $i<k$; furthermore,
    \[
      |s_n|
        \leq
      M^i(x_n,|s_n|)
        <
      M^i(x_n,|s_n|)+1
        \leq
      M^{i+1}(x_n,|s_n|)
        <
      M^{i+1}(x_n,|s_n|)+1
        \leq
      |s_{n+1}|
    \]
  so the second coordinate of $\pmb q(n)$ is always strictly increasing.

  By the definition of $\tau$,
    \[
      \pmb q((k+1)n)
        =
      \pmb p(n)
        \not\in
      \bigcup_{m\leq n}
      \tau(\pmb p\rest^1 m)
        \supseteq
      \bigcup_{m\leq (k+1)n}
      \sigma(\pmb q\rest^{k+1} m)
    \]

  Since
    \[
      \pmb q((k+1)n+(i+1))
        =
      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
        \in
      X\times A
    \]
  it follows that $\pmb q((k+1)n+(i+1))\not\in K'_F$ for any
  $F\in[\omega_1]^{<\omega}$.

  Then it's sufficient to note that
    \[
      |a_{M^{i+1}(x_n,|s_n|)}|
        =
      M^{i+1}(x_n,|s_n|) + 1
        >
      m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)
    \]
  to show that
    \[
      \pmb q((k+1)n+(i+1))
        =
      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
        \not\in
      L_{m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)}
    \]
  and therefore $\pmb q((k+1)n+(i+1))$ is a legal move.

  As a result, $\pmb q$ is a legal attack against $\sigma$, and
  $\{\{\pmb q(n)\}:n<\omega\}\supseteq\{\{\pmb p(n)\}:n<\omega\}$ are
  both locally finite.

  Finally, if the range of $\pmb p$ intersects $C$, those moves may be safely
  ignored as they cannot be repeated and lay in a closed discrete set,
  so the proof is complete.
\end{proof}

Therefore if $\pmb X$ can be constructed which is not metacompact, then
$\pl K$ lacks a $k$-Markov strategy for any $k<\omega$.

\begin{thm}
  $\pmb X$ is metacompact
    if and only if
  $\{U_\alpha:\alpha<\omega_1\}$ is $\sigma$-point-finite.
\end{thm}

\begin{proof}
  Let $\omega_1=\bigcup_{n<\omega}A_n$ such that
  $\{U_\alpha:\alpha\in A_n\}$ is point-finite for each $n<\omega$.

  Let $\mc U$ be a cover of $\pmb X$, and for each $s\in 2^\omega$
  let $\mc V_s$ be a finite open refinement of $\mc C$ covering the compact
  set $X\times\{s\}$. Then let $\mc W_n = \{B_{\alpha,n_\alpha}:\alpha\in A_n\}$
  be an open refinement of $\mc C$ for each $n<\omega$, and note that it
  is point-finite. It follows that
  $\mc U' = \bigcup_{s\in 2^{<\omega}} \mc V_s \cup \bigcup_{n<\omega} \mc W_n$
  is an open $\sigma$-point-finite refinement of $\mc U$, so $\pmb X$
  is $\sigma$-metacompact, and therefore it is metacompact.

  For the other direction, consider the open cover
  $\mc U = \{B_{\alpha,0}:\alpha<\omega_1\}$ of the closed subset $C$ of
  metacompact $\pmb X$, and let $\{B_{\alpha,n_\alpha}:\alpha<\omega_1\}$ be
  a point-finite refinement. Then
  $\mc U_s = \{ U_\alpha : c_\alpha \rest n_\alpha = s\}$ is
  point-finite for $s\in 2^{<\omega}$ and
  $U_\alpha\in\mc U_{c_\alpha\rest n_\alpha}$ for each $\alpha<\omega_1$.
  Therefore $\mc U = \bigcup_{s\in 2^{<\omega}} \mc U_s$ is
  $\sigma$-point-finite.
\end{proof}

The following example was suggested by Gary Gruenhage.

\begin{thm}
  There exists a compact, zero-dimensional topological space $X$
  with a clopen cover $\{U_\alpha : \alpha<\omega_1\}$ of distinct
  sets which is not $\sigma$-point-finite.
\end{thm}

\begin{proof}
  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
  compact; one such space was constructed in \cite{Marciszewski1991291}.
  Let $X=Y^2$.
  Then by characterizations of Corson and Eberlien compacts found in
  \cite{MR752278},
  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
  clopen cover of $X$ which is not $\sigma$-point-finite.
\end{proof}

\begin{cor}
  There exists a locally compact space $X$ such that $\pl K\win\gruKPGame{X}$
  but $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
\end{cor}

So the following questions remain open:

\begin{ques}
  Does $\pl K\ktactwin{k+1}\gruKPGame{X}$ imply
  $\pl K\tactwin\gruKPGame{X}$ for all locally compact spaces?
  Equivalently, is metacompactness characterized by
  $\pl K\ktactwin{k+1}\gruKPGame{X}$ for all locally compact spaces?
  What about for Markov strategies and $\sigma$-metacompactness?
\end{ques}
