\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newcommand{\rest}{\upharpoonright}
\newcommand{\term}{\textbf}

\title{On constructing permutation-fair dice}
\author{Steven Clontz}
\begin{document}
\maketitle

By convention, \(n=\{0,1,\dots,n-1\}\) for each natural number \(n\).

\begin{definition}
    A function \(F:n\to S\) is called a \term{formula} for a 
    set \(S\) of dice, where \(F(k)\) returns which die in the set \(S\)
    has a face with the number \(k<n\).
\end{definition}

For example, the formula \(F:4\to\{A,B\}\) defined by \(ABBA\)
represents an assignment of values to the faces of dice in the set \(\{A,B\}\).
In particular \(A\) has two sides \(\{0,3\}\) while die \(B\) has sides \(\{1,2\}\).

\begin{definition}
    Given a formula \(F:n\to S\) and \(T\subseteq S\), let \(F_T:m\to T\) be the 
    \term{subformula} obtained by removing the dice in \(S\setminus T\) from the sequence.
\end{definition}

So for \(F:7\to\{A,B,C\}\) defined by \(ABCACBA\), \(F_{\{A,C\}}\) is defined by
\(ACACA\).

\begin{definition}
    Given a sequence \(F:n\to S\) and \(m\leq n\), let \(F\rest m:m\to S\) be the 
    \term{restriction sequence} where \((F\rest m)(k)=F(k)\) for \(k<m\).
\end{definition}

So for \(F:7\to\{A,B,C\}\) defined by \(ABCACBA\), \(F\rest 4\) is defined by
\(ABCA\).

\begin{definition}
    A \term{sample} for a formula \(F:n\to S\) is a function \(s:S\to n\) such
    that \(F(s(A))=A\) for all \(A\in S\). Let \(\sigma (F)\) collect
    all samples for the formula \(F\).
\end{definition}

\begin{definition}
    The \term{result} of a sample \(s:S\to n\) is a permutation \(r_s:|S|\to S\)
    of \(S\) such that \(i\leq j\) if and only if \(f(r_s(i))\leq f(r_s(j))\).
\end{definition}

So for the formula \(ABCACBA\), a sample might be defined
by \(f(A)=3,f(B)=2,f(C)=4\), yielding the result \(BAC\).
Note that the highest-valued die in the sample \(s\) is given by \(r_s(|S|-1)\).

\begin{definition}
    A formula \(F:n\to S\) is called \term{permutation-fair} if
    for all permutations \(p,q\) of \(S\),
    \(|\{s\in\sigma (F):r_s=p\}|=|\{s\in\sigma (F):r_s=q\}|\). 
\end{definition}

\begin{definition}
    A formula \(F:n\to S\) is called \term{go-first-fair} if
    for all \(A,B\in S\),
    \(|\{s\in\sigma (F):r_s(|S|-1)=A\}|=|\{s\in\sigma (F):r_s(|S|-1)=B\}|\). 
\end{definition}

\begin{proposition}
    Suppose \(F:n\to S\) is a permutation-fair (resp. go-first-fair)
    formula. Then \(F_T\) is permutation-fair (resp. go-first-fair)
    for all \(T\subseteq S\).
\end{proposition}

\begin{theorem}
    Suppose \(F:n\to S\cup\{X\}\) is a go-first-fair formula such that 
    \(F_S\) is permutation fair, and for each \(m\leq n\) where \(f(m)=X\), 
    \((F\rest m)_S\) is permutation-fair.
    Then \(F\) is permutation-fair.
\end{theorem}

\begin{proof}
    Since go-first-fair implies permutation-fair in the base case \(|S|=0\),
    assume the theorem holds when \(|S|\leq k\), and let \(|S|=k+1\).
    
    For each \(T\subsetneq S\), we note that \(F_{T\cup\{X\}}\) is a go-first-fair 
    formula such that for each \(m\leq|F_{T\cup\{X\}}|\) where \(F_{T\cup\{X\}}(m)=X\), 
    \(F_{T\cup\{X\}}\rest m=F\rest m'\) for some \(m\leq m'< n\) and
    \(F(m')=X\). Thus \((F_{T\cup\{X\}}\rest m)_T=(F\rest m')_T=((F\rest m')_S)_T\)
    is permutation-fair, and since \(|T|\leq k\), \(F_{T\cup\{X\}}\) is permutation-fair.

    So let \(p,q\) be permutations of \(S\cup\{X\}\); we aim to show that
    \(|\{s\in\sigma (F):r_s=p\}|=|\{s\in\sigma (F):r_s=q\}|\). 
    
    First, suppose \(p(|S|)=q(|S|)=X\). Thus 
    \[
        |\{s\in\sigma (F):r_s=p\}|
    =
        \sum\Big\{\Big|\{s\in\sigma ((F\rest m)_S):r_s=p\rest|S|\}\Big|:f(m)=X\Big\}
    \] 
    and likewise for \(q\). Since \((F\rest m)_S\) is permutation-fair,
    \[
        |\{s\in\sigma ((F\rest m)_S):r_s=p\rest|S|\}|
    =
        |\{s\in\sigma ((F\rest m)_S):r_s=q\rest|S|\}|
    \]
    so the result follows in this case.


\end{proof}
\end{document}
