\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{tikz}
\usetikzlibrary{arrows}

\usepackage{../../clontzDefinitions}

\renewcommand{\vec}{\mathbf}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{notation}[theorem]{Notation}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

      \theoremstyle{plain}
      \newtheorem*{theorem*}{Theorem}
      \newtheorem*{lemma*}{Lemma}
      \newtheorem*{corollary*}{Corollary}
      \newtheorem*{proposition*}{Proposition}
      \newtheorem*{conjecture*}{Conjecture}
      \newtheorem*{question*}{Question}
      \newtheorem*{claim*}{Claim}

      \theoremstyle{definition}
      \newtheorem*{definition*}{Definition}
      \newtheorem*{example*}{Example}
      \newtheorem*{game*}{Game}

      \theoremstyle{remark}
      \newtheorem*{remark*}{Remark}


\usepackage{lineno}
\linenumbers



\begin{document}

\title{Coding Strategies in Baker's Game}



\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36688}
\email{sclontz@southalabama.edu}



\keywords{Selection principle, selection game,
limited information strategies}

\subjclass[2010]{54D20, 54D45, 91A44}



\begin{abstract}
TODO
\end{abstract}


\maketitle




\begin{abstract}
TODO
\end{abstract}


\maketitle



Let \(f^\leftarrow(y)=\setB{x\in A}{f(x)=y}\).

\begin{proposition}\label{denseThreads}
There exists a function \(f:\mathbb R\to\mathbb R^{<\omega}\) such that
for each \(s\in\mathbb R^{<\omega}\), \(f^\leftarrow(s)\) is dense in \(\mathbb R\).
\end{proposition}

\begin{proof}
Noting that \(|\mathbb R^{<\omega}|=|\mathbb R|=\mathfrak c\), we recall that
\(\mathbb R\) may be partitioned into \(\mathfrak c\)-many parts, each dense in
\(\mathbb R\) (e.g., the equivalence classes of \(x\sim y\) iff \(x-y\in\mathbb Q\)).
We may then let \(f\) assign each equivalence class to a distinct sequence in
\(\mathbb R^{<\omega}\).
\end{proof}

(We thank Lynne Yengulalp for
suggesting the partition result that greatly simplified the preceding proof.)



\begin{theorem}
\(\plII\win G(W)\) if and only if \(\plII\codewin G(W)\).
\end{theorem}
\begin{proof}
We need only show 
\(\plII\notcodewin G(W)\) implies \(\plII\notwin G(W)\).
Let \(\sigma\) be a perfect-information strategy for \(\plII\),
and let \(f\) be given by Prop \ref{denseThreads}.

First, we choose
\[
\tau(\tuple{a_0})\in
\big(a_0,\sigma(\tuple{a_0})\big)\cap
f^\leftarrow\big(\tuple{a_0}\big)
\]
that is, we guarantee \(a_0<\tau(\tuple{a_0})<\sigma(\tuple{a_0})\)
and \(f\big(\tau(\tuple{a_0})\big)=\tuple{a_0}\).

Given \(b_n,a_{n+1}\), define
\(b_n'=\min\big(b_n,\sigma(f(b_n)\concat\tuple{a_{n+1}})\big)\),
noting \(a_{n+1}<b_n'\). Now choose
\[
\tau(\tuple{b_n,a_{n+1}})\in
\big(a_{n+1},b'\big)\cap
f^\leftarrow\big(f(b_n)\concat\tuple{a_{n+1}}\big)
\]
that is, we guarantee
\(a_{n+1}<\tau(\tuple{b_n,a_{n+1}})<b_n'\leq b_n\) and
\(f\big(\tau(\tuple{b_n,a_{n+1}})\big)=f(b_n)\concat\tuple{a_{n+1}}\).

Then \(\tau\) defines a coding strategy for \(\plII\); suppose it is
defeated by \(\plI\) choosing \(a_n\) during round \(n\).

Then if \(b_n\) is the move designated by \(\tau\) for player \(\plII\)
during round \(n\), that is, \(b_0=\tau(\tuple{a_0})\) and
\(b_{n+1}=\tau(\tuple{b_n,a_{n+1}})\),
we have \(f(b_n)=\tuple{a_0,\dots,a_n}\).

First, we see that
\[a_0<a_1<\tau(\tuple{a_0})<\sigma(\tuple{a_0})\]

And finally, we see that
\[a_{n+1}<a_{n+2}<\tau(\tuple{b_n,a_{n+1}})<b_n'\leq
\sigma(f(b_n)\concat\tuple{a_{n+1}})=\sigma(\tuple{a_0,\dots,a_{n+1}})\]

Therefore we have shown that \(a_n\) is also a legal move against the
perfect information strategy \(\sigma\) each round, and therefore
\(\sigma\) is also not a winning strategy.
\end{proof}


\end{document}



\section{TODO}

\begin{definition}
  An \term{\(\omega\)-length game} is a pair \(G=\<M,W\>\) such that
  \(W\subseteq M^\omega\). The set \(M\) is the \term{moveset} of the game,
  and the set \(W\) is the \term{payoff set} for the second player.
\end{definition}

In such a game \(G\), players \(\plI\)\end{proof}


\end{document}



\section{TODO}

\begin{definition}
  An \term{\(\omega\)-length game} is a pair \(G=\<M,W\>\) such that
  \(W\subseteq M^\omega\). The set \(M\) is the \term{moveset} of the game,
  and the set \(W\) is the \term{payoff set} for the second player.
\end{definition}

In such a game \(G\), players \(\plI\) and \(\plII\) alternate making choices
\(a_n\in M\) and \(b_n\in M\) during each round \(n<\omega\), 
and \(\plII\) wins the game if and only if \(\<a_0,b_0,a_1,b_1,\dots\>\in W\).

Often when defining games, \(\plI\) and \(\plII\) alternate making choices
\(a_n\in M\) and \(b_n\in M\) during each round \(n<\omega\), 
and \(\plII\) wins the game if and only if \(\<a_0,b_0,a_1,b_1,\dots\>\in W\).

Often when defining games, \(\plI\) and \(\plII\) are restricted to choosing
from different movesets \(A,B\). Of course, this can be modeled with \(\<M,W\>\)
by simply letting \(M=A\cup B\) and adding/removing sequences from \(W\)
whenever player \(\plI\)/\(\plII\) makes the first ``illegal'' move.

A class of such games heavily studied in the literature, particularly
topology (see \cite{MR1378387} and its
many sequels), are selection games.

\begin{definition}
  The \term{selection game} \(\schStrongSelGame{\mc A}{\mc B}\) 
  is an \(\omega\)-length game involving Players \(\plI\) and \(\plII\). 
  During round \(n\), \(\plI\) chooses
  \(A_n\in\mc A\), followed by \(\plII\) choosing \(B_n\in A_n\).
  Player \(\plII\) wins in the case that \(\{B_n:n<\omega\}\in\mc B\),
  and Player \(\plI\) wins otherwise.
\end{definition}

  Let \(\mc P(Z)=\{z:z\subseteq Z\}\) denote the power set of \(Z\),
  so \(\{B_n:n<\omega\}\in\mc P(\bigcup\mc A)\) for any choices
  \(B_n\in A_n\in\mc A\) made by the players.
  Then for brevity, let 
  \[
    \schStrongSelGame{\mc A}{\neg \mc B}
      =
    \schStrongSelGame{\mc A}{\mc P\left(\bigcup \mc A\right)\setminus \mc B}
  .\]
  That is, this is the analogous game where
  \(\plII\) wins provided \(\{B_n:n<\omega\}\not\in\mc B\),
  and \(\plI\) wins otherwise.

\begin{notation}
  For a set \(X\), let \(\mathbf C(X)=\{f\in(\bigcup X)^X:x\in X\Rightarrow f(x)\in x\}\)
  be the collection of all choice functions on \(X\).
\end{notation}

\begin{definition}
  Write \(X\preceq Y\) if \(X\) is coinitial in \(Y\) with respect to \(\subseteq\);
  that is, \(X\subseteq Y\), and for all \(y\in Y\), there exists \(x\in X\) such that 
  \(x\subseteq y\).

  In the context of selection games, we will say \(\mc A'\) is a \term{selection basis}
  for \(\mc A\) when \(\mc A'\preceq \mc A\).
\end{definition}

\begin{definition}
  The set \(\mc R\) is said to be a \term{reflection} of the set \(\mc A\)
  if \[\{\ran f:f\in\mathbf C(\mc R)\}\] is a selection basis for \(\mc A\).
\end{definition}

Put another way, \(\mc R\) is a reflection of \(\mc A\) if \(\ran f\in\mc A\) 
for all \(f\in\mathbf C(\mc R)\), and for each \(A\in\mc A\) there exists
\(f_A\in\mathbf C(\mc R)\) such that \(\ran{f_A}\subseteq A\).

As we will see, reflections of selection sets are used frequently (but implicitly) 
throughout the literature to define dual selection games.

We use the following conventions to describe strategies for playing games.

\begin{notation}
  For \(f\in B^A\) and \(X\subseteq A\), let \(f\rest X\) be the restriction of \(f\)
  to \(X\). In particular, for \(f\in B^\omega\) and \(n<\omega\), \(f\rest n\)
  describes the first \(n\) terms of the sequence \(f\).
\end{notation}

\begin{definition}
  A \term{strategy} for the first player \(\plI\) (resp. second player \(\plII\))
  in a game \(G\) with moveset \(M\) is a function
  \(\sigma:M^{<\omega}\to M\). This strategy is said to be \term{winning} if
  for all possible \term{attacks} \(\alpha\in M^\omega\) by their opponent,
  where \(\alpha(n)\) is played by the opponent during round \(n\),
  the player wins the game by playing \(\sigma(\alpha\rest n)\)
  (resp. \(\sigma(\alpha\rest n+1)\)) during round \(n\).
\end{definition}

That is, a strategy is a rule that determines the moves of a player based upon
all previous moves of the opponent. (It could also rely on all previous
moves of the player using the strategy, since these can be reconstructed from
the previous moves of the opponent and the strategy itself.)

\begin{definition}
  A \term{predetermined strategy} for the first player \(\plI\)
  in a game \(G\) with moveset \(M\) is a function
  \(\sigma:\omega\to M\). This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the first player wins the game by playing \(\sigma(n)\)
  during round \(n\).
\end{definition}

So a predetermined strategy ignores all moves of the opponent during the
game (all moves were decided before the game began). Such strategies
are also known as \(0\)-Markov strategies or \(0\)-Markov tactics.
The following definition is similarly also known as a \(1\)-Markov strategy.

\begin{definition}
  A \term{Markov strategy} for the second player \(\plII\)
  in a game \(G\) with moveset \(M\) is a function
  \(\sigma:M\times\omega\to M\). This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the second player wins the game by playing \(\sigma(\alpha(n),n)\)
  during round \(n\).
\end{definition}

So a Markov strategy may only consider the most recent move of the opponent,
and the current round number. Note that unlike perfect-information or
predetermined strategies, a Markov strategy cannot use knowledge of
moves used previously by the player (since they depend on previous moves of
the opponent that have been ``forgotten'').

We also consider similar strategies that ignore the round number.

\begin{definition}
  A \term{constant strategy} for the first player \(\plI\)
  in a game \(G\) with moveset \(M\) is simply a choice \(m\in M\).
  This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the first player wins the game by playing \(m\) during every round.
\end{definition}

\begin{definition}
  A \term{tactical strategy} for the second player \(\plII\)
  in a game \(G\) with moveset \(M\) is a function
  \(\sigma:M\to M\). This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the second player wins the game by playing \(\sigma(\alpha(n))\)
  during round \(n\).
\end{definition}

\begin{notation}
  Write \(\plI\win G\) (resp. \(\plI\prewin G\), \(\plI\conwin G\)) 
  if player \(\plI\) has a winning
  strategy (resp. winning predetermined/constant strategy) for the game \(G\). Similarly,
  write \(\plII\win G\) (resp. \(\plII\markwin G\), \(\plII\tactwin G\)) 
  if player \(\plII\) has a winning
  strategy (resp. winning Markov/tactical strategy) for the game \(G\).
\end{notation}

Of course: 
\[
  \plII\tactwin G\Rightarrow 
  \plII\markwin G\Rightarrow 
  \plII\win G\Rightarrow 
  \plI\notwin G\Rightarrow 
  \plI\notprewin G\Rightarrow 
  \plI\notconwin G
.\]
In general, none of these implications (not even the middle \cite{MR0054922}) can be reversed.

While predetermined and constant strategies are rarely explicitly studied in the literature,
they are implicitly considered when studying the following well-known principles.

\begin{definition}[\cite{MR1378387}]
  The selection principle \(\schStrongSelProp{\mc A}{\mc B}\) asserts
  that for each sequence \(\setB{A_n}{n<\omega}\in[\mc A]^\omega\),
  there exist \(B_n\in A_n\) such that \(\setB{B_n}{n<\omega}\in\mc B\).
\end{definition}

For example, if \(\mc O_X\) denotes the open covers of a space \(X\), 
then \(\schStrongSelProp{\mc O_X}{\mc O_X}\) is the Rothberger covering property.

\begin{definition}[\cite{MR2363173}]
  The choice principle \(\binom{\mc A}{\mc B}^\kappa\) asserts
  that for each \(A\in \mc A\), there exists a subset
  \(B\subseteq A\) where \(|B|=\kappa\) and \(B\in\mc B\).
  (When \(\kappa\) is omitted, the criterion \(|B|=\kappa\) is also omitted.)
\end{definition}

For example,
\(\binom{\mc O_X}{\mc O_X}^\omega\) is the Lindel\"of covering property.

\begin{proposition}
  \(\schStrongSelProp{\mc A}{\mc B}\) is equivalent to
  \(\plI\notprewin \schStrongSelGame{\mc A}{\mc B}\), and
  \(\binom{\mc A}{\mc B}^\omega\) is equivalent to
  \(\plI\notconwin \schStrongSelGame{\mc A}{\mc B}\).
\end{proposition}

\begin{proof}
  The first equivalence is direct from their defintions.

  To see the second,
  assume \(\binom{\mc A}{\mc B}^\omega\). Then given a constant strategy
  \(A\in\mc A\) for \(\plI\), \(\plII\) uses \(\binom{\mc A}{\mc B}^\omega\) to
  choose \(B=\setB{b_n}{n<\omega}\subseteq A\) where \(B\in\mc B\); thus
  playing \(b_n\) in round
  \(n\) defeats \(\plI\)'s constant strategy.

  Likewise, assuming 
  \(\plI\notconwin \schStrongSelGame{\mc A}{\mc B}\), for each constant strategy
  \(A\in\mc A\) for \(\plI\) there must be a counterattack playing \(b_n\in A\)
  during each round \(n\) such that \(\setB{b_n}{n<\omega}\in\mc B\); this witnesses
  \(\binom{\mc A}{\mc B}^\omega\).
\end{proof}

The goal of this paper is to characterize when two games are ``dual'' in the following
senses.

\begin{definition}
  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
  are \term{tactical information dual} if both
  of the following hold.
  \begin{itemize}
    \item \(I\conwin G(X)\) if and only if \(II\tactwin H(X)\).
    \item \(II\tactwin G(X)\) if and only if \(I\conwin H(X)\).
  \end{itemize}
\end{definition}

\begin{definition}
  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
  are \term{Markov information dual} if both
  of the following hold.
  \begin{itemize}
    \item \(I\prewin G(X)\) if and only if \(II\markwin H(X)\).
    \item \(II\markwin G(X)\) if and only if \(I\prewin H(X)\).
  \end{itemize}
\end{definition}

\begin{definition}
  A pair of games \(G(X),H(X)\) defeind for a topological space \(X\)
  are \term{perfect information dual} if both
  of the following hold.
  \begin{itemize}
    \item \(I\win G(X)\) if and only if \(II\win H(X)\).
    \item \(II\win G(X)\) if and only if \(I\win H(X)\).
  \end{itemize}
\end{definition}

\begin{definition}
  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
  are \term{dual} if they are tactial, Markov, and perfect information
  dual.
\end{definition}

\section{Main Results}

The following six theorems demonstrate that reflections characterize
dual selection games for perfect information strategies and
certain limited information strategies.

For example,
the duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
and the point-open game on \(X\) for perfect information strategies
was first noted by Galvin in \cite{MR0493925}, and
for Markov-information strategies by Clontz and Holshouser in
\cite{CLONTZ2019106815}. These proofs may be generalized as follows.

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\). 

  Then
  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(A\) witness 
  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(A\in\mc A\),
  \(\ran{\tau}\subseteq A\)
  for some \(\tau\in\mathbf C(\mc R)\). 
  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
  Note that since \(A\) is winning and 
  \(\tau(R_n)\in\ran{\tau}\subseteq A\),
  \(\{\tau(R_n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Then \(\sigma\in\mathbf C(\mc R)\) and we may let
  \(A=\ran{\sigma}\in\mc A\). 
  Suppose that \(B_n\in A=\ran{\sigma}\) for
  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
  \(B_n=\sigma(R_n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(A\) witnesses
  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\). 

  Then
  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\).
  Suppose that for each \(R\in\mc R\),
  there was \(g(R)\in R\) such that for all \(A\in \mc A\),
  \(\sigma(A)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\)
  and \(\ran g\in\mc A\),
  thus \(\sigma(\ran g)\not=g(R)\) for all \(R\in\mc R\),
  a contradiction.

  So choose \(R\in\mc R\) such that for all \(r\in R\)
  there exists \(A_r\in\mc A\) such that \(\sigma(A_r)=r\).
  It follows that when \(r_n\in R\) for \(n<\omega\),
  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n}):n<\omega\}\in B\),
  so \(R\) witnesses
  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(R\) witness 
  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Then \(R\in\mc R\), so for \(A\in\mc A\), let
  \(f_A\in\mathbf C(\mc R)\) satisfy \(\ran{f_A}\subseteq A\),
  and let \(\tau(A)=f_A(R)\in A\cap R\).
  Then if \(A_n\in\mc A\) for \(n<\omega\), \(\tau(A_n)\in R\),
  so \(\{\tau(A_n):n<\omega\}\in\mc B\).
  Thus \(\tau\) witnesses
  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\). 

  Then
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(\sigma(n)\in\mc A\),
  \(\ran{f_n}\subseteq\sigma(n)\)
  for some \(f_n\in\mathbf C(\mc R)\). So let
  \(\tau(R,n)=f_n(R)\) for all \(R\in \mc R\) and \(n<\omega\).
  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
  Note that since \(\sigma\) is winning and 
  \(\tau(R_n,n)=f_n(R_n)\in\ran{f_n}\subseteq\sigma(n)\),
  \(\{\tau(R_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\),
  and let \(\tau(n)=\ran{f_n}\in\mc A\). 
  Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\). 

  Then
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
  Let \(n<\omega\). Suppose that for each \(R\in\mc R\),
  there was \(g(R)\in R\) such that for all \(A\in \mc A\),
  \(\sigma(A,n)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\)
  and \(\ran g\in\mc A\),
  thus \(\sigma(\ran g,n)\not=g(R)\) for all \(R\in\mc R\),
  a contradiction.

  So choose \(\tau(n)\in\mc R\) such that for all \(r\in \tau(n)\)
  there exists \(A_{r,n}\in\mc A\) such that \(\sigma(A_{r,n},n)=r\).
  It follows that when \(r_n\in\tau(n)\) for \(n<\omega\),
  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n,n}):n<\omega\}\in B\),
  so \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Then \(\sigma(n)\in\mc R\), so for \(A\in\mc A\), let
  \(f_A\in\mathbf C(\mc R)\) satisfy \(\ran{f_A}\subseteq A\),
  and let \(\tau(A,n)=f_A(\sigma(n))\in A\cap\sigma(n)\).
  Then if \(A_n\in\mc A\) for \(n<\omega\), \(\tau(A_n,n)\in\sigma(n)\),
  so \(\{\tau(A_n,n):n<\omega\}\in\mc B\).
  Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\). 

  Then
  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\).
  Let \(c(\emptyset)=\emptyset\). Suppose 
  \(c(s)\in(\bigcup A)^{<\omega}\)
  is defined for \(s\in\mc R^{<\omega}\). Since \(\sigma(c(s))\in\mc A\),
  let \(f_s\in\mathbf C(\mc R)\) satisfy \(\ran{f_s}\subseteq\sigma(c(s))\),
  and let \(c(s\concat\<R\>)=c(s)\concat\<f_s(R)\>\).
  Then let \(c(\alpha)=\bigcup\{c(\alpha\rest n):n<\omega\}\)
  for \(\alpha\in\mc R^\omega\), so
  \[
    c(\alpha)(n)
      =
    f_{\alpha\rest n}(\alpha(n))
      \in
    \ran{f_{\alpha\rest n}}
      \subseteq
    \sigma(c(\alpha\rest n))
  \]
  demonstrating that \(c(\alpha)\) is a legal attack against \(\sigma\).

  Let \(\tau(s\concat\<R\>)=f_s(R)\). Consider the attack \(\alpha\in\mc R^\omega\)
  against \(\tau\). Then since \(\sigma\) is winning and
  \(
    \tau(\alpha\rest n+1)=f_{\alpha\rest n}(\alpha(n))\in
    \ran{f_{\alpha\rest n}}\subseteq\sigma(c(\alpha\rest n))
  \), it follows that \(\{\tau(\alpha\rest n+1):n<\omega\}\not\in\mc B\).
  Thus \(\tau\) witnesses
  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).
  For \(s\in \mc R^{<\omega}\), define \(f_s\in\mathbf C(\mc R)\)
  by \(f_s(R)=\sigma(s\concat\<R\>)\). Let \(\tau(\emptyset)=\ran{f_\emptyset}\in\mc A\),
  and for \(x\in\tau(\emptyset)\), choose \(R_{\<x\>}\in\mc R\) such that
  \(x=f_{\emptyset}(R_{\<x\>})\) (for other \(x\in\bigcup A\), choose \(R_{\<x\>}\)
  arbitrarily as it won't be used). Now let \(s\in(\bigcup A)^{<\omega}\),
  and suppose \(R_{s\rest n\concat\<x\>}\in\mc R\) has been defined for
  \(n\leq|s|\) and \(x\in\bigcup A\). 
  Then let \(\tau(s\concat\<x\>)=\ran{f_{\<R_{s\rest 0},\dots,R_s,R_{s\concat\<x\>}\>}}\)
  and for \(y\in\tau(s)\) choose \(R_{s\concat\<x,y\>}\) such that
  \(x=f_{\<R_{s\rest 0},\dots,R_s,R_{s\concat\<x\>}\>}(R_{s\concat\<x,y\>})\) (and again,
  choose \(R_{s\concat\<x,y\>}\) arbitrarily for other \(y\in\bigcup\mc A\) as it won't be used).

  Then let \(\alpha\) attack \(\tau\), so
  \(\alpha(n)\in\tau(\alpha\rest n)\) and thus 
  \(\alpha(n)=f_{\<R_{\alpha\rest 0},\dots,R_{\alpha\rest n}\>}(R_{\alpha\rest n+1})
  =\sigma(\<R_{\alpha\rest 0},\dots,R_{\alpha\rest n+1}\>)\).  Since \(\sigma\) is winning,
  \(\{\sigma(\<R_{\alpha\rest 0},\dots,R_{\alpha\rest n+1}\>):n<\omega\}
  =\{\alpha(n):n<\omega\}\not\in\mc B\).
  Thus \(\tau\) witnesses
  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{theorem}
  Let \(\mc R\) be a reflection of \(\mc A\). 

  Then
  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plI\win\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\).
  Let \(s\in(\bigcup A)^{<\omega}\) and assume \(a(s)\in\mc A^{|s|}\) is defined
  (of course, \(a(\emptyset)=\emptyset\)).
  Suppose for all \(R\in\mc R\) there existed \(f(R)\in R\) such that for all
  \(A\in\mc A\), \(\sigma(a(s)\concat\<A\>)\not=f(R)\). Then
  \(f\in\mathbf C(\mc R)\) and \(\ran{f}\in\mc A\), and thus 
  \(\sigma(a(s)\concat\<\ran{f}\>)\not=f(R)\) for all \(R\in\mc R\), a contradiction.
  So let \(\tau(s)\in\mc R\) satisfy for all \(x\in\tau(s)\) there exists
  \(a(s\concat\<x\>)\in\mc A^{|s|+1}\) extending \(a(s)\) such that 
  \(x=\sigma(a(s\concat\<x\>))\).

  If \(\tau\) is attacked by \(\alpha\in(\bigcup R)^\omega\), then 
  \(\alpha(n)\in\tau(\alpha\rest n)\). So \(\alpha(n)=\sigma(a(\alpha\rest n+1))\),
  and since \(\sigma\) is winning, 
  \(\{\sigma(a(\alpha\rest n+1)):n<\omega\}=\{\alpha(n):n<\omega\}\in\mc B\).
  Therefore \(\tau\) witnesses
  \(\plI\win\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plI\win\schStrongSelGame{\mc R}{\neg\mc B}\).
  Let \(s\in\mc A^{<\omega}\), and suppose \(r(s)\in(\bigcup \mc R)^{|s|}\) is defined
  (again, \(r(\emptyset)=\emptyset\)). For \(A\in\mc A\) choose \(f_A\in\mathbf C(\mc R)\)
  where \(\ran{f_A}\subseteq A\), and let \(\tau(s\concat\<A\>)=f_A(\sigma(r(s)))\),
  and let \(r(s\concat\<A\>)\) extend \(r(s)\) by letting
  \(r(s\concat\<A\>)(|s|)=\tau(s\concat\<A\>)\).

  If \(\tau\) is attacked by \(\alpha\in\mc A^\omega\), 
  then since \(\tau(\alpha\rest n+1)=f_{\alpha(n)}(\sigma(r(\alpha\rest n))\in\alpha(n)\cap\sigma(r(\alpha\rest n))\)
  and \(\sigma\) is winning, we conclude that \(\tau\) is a legal strategy and
  \(\{\tau(\alpha\rest n+1):n<\omega\}\in\mc B\).
  Therefore \(\tau\) witnesses
  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\begin{corollary}\label{mainResult}
  If \(\mc R\) is a reflection of \(\mc A\),
  then \(\schStrongSelGame{\mc A}{\mc B}\) and \(\schStrongSelGame{\mc R}{\neg\mc B}\)
  are  dual.
\end{corollary}

\section{Applications of Reflections}

\begin{definition}\label{selectionSets}
  Let \(X\) be a topological space and \(\mc T_X\) be a chosen basis of nonempty sets for its topology.
  \begin{itemize}
    \item Let \(\mc T_{X,x} = \{U\in\mc T_X : x\in U\}\) be the local point-base at \(x\in X\).
    \item Let \(\Omega_{X,x} = \{Y\subseteq X: \forall U\in\mc T_{X,x}(U\cap Y\not=\emptyset)\}\) be the fan at \(x\in X\).
    \item Let \(\mc T_{X,F} = \{U\in\mc T_X : F\subseteq U\}\) be the local finite-base at \(F\in[X]^{<\aleph_0}\).
    \item Let \(\mc O_X = \{\mc U\subseteq\mc T_X : \bigcup \mc U=X\}\) be the collection
          of basic open covers of \(X\).
    \item Let \(\mc P_X = \{\mc T_{X,x} : x\in X\}\) be the collection of local point-bases of \(X\).
    \item Let \(\Omega_X = \{\mc U\subseteq\mc T_X : \forall F\in[X]^{<\aleph_0}\exists U\in\mc U(F\subseteq U)\}\)
          be the collection of basic \(\omega\)-covers of \(X\).
    \item Let \(\mc F_X = \{\mc T_{X,F} : F\in [X]^{<\aleph_0}\}\) be the collection of local finite-bases of \(X\).
    \item Let \(\mc D_X = \{Y\subseteq X: \forall U\in\mc T_X(U\cap Y\not=\emptyset)\}\) be the collection of dense subsets of \(X\).
    \item Let \(\Gamma_{X,x} = \{Y\subseteq X: \forall U\in\mc T_{X,x}(Y\setminus U\in[X]^{<\aleph_0})\}\) be the collection
          of converging fans at \(x\in X\). (When intersected with \([X]^{\aleph_0}\), these are the non-trivial
          sequences of \(X\) converging to \(x\).)
  \end{itemize}
\end{definition}

%While these notions were defined in terms of a particular basis, the reader may verify the the following.
%
%\begin{proposition}
%  Let \(\mc A'\) be a selection basis for \(\mc A\).
%  \begin{itemize}
%    \item \(\plI\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\win\schStrongSelGame{\mc A'}{\mc B}\).
%    \item \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\prewin\schStrongSelGame{\mc A'}{\mc B}\).
%    \item \(\plII\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\win\schStrongSelGame{\mc A'}{\mc B}\).
%    \item \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\markwin\schStrongSelGame{\mc A'}{\mc B}\).
%  \end{itemize}
%\end{proposition}
%
%\begin{proposition}
%  Each selection set in Definition \ref{selectionSets} is a selection basis for the set
%  defined by replacing \(\mc T_X\) with the set of all nonempty open sets in \(X\).
%\end{proposition}
%
%As such, the choice of topological basis is irrelevant when playing selection games using these sets.

We may now establish the following dual games.

\begin{proposition}
  \(\mc P_X\) is a reflection of \(\mc O_X\).
\end{proposition}
\begin{proof}
  For every basic open cover \(\mc U\), the corresponding choice function \(f_{\mc U}\in\mathbf C(\mc P_X)\) is simply
  the witness that for each \(\mc T_{X,x}\in\mc P_X\), there exists \(f_{\mc U}(\mc T_{X,x})\in\mc U\) such that
  \(x\in f_{\mc U}(\mc T_{X,x})\).
\end{proof}

\begin{corollary}\label{coverSel1}
  \(\schStrongSelGame{\mc O_X}{\mc B}\) and \(\schStrongSelGame{\mc P_X}{\neg\mc B}\) are dual.
\end{corollary}

In the case that \(\mc B=\mc O_X\), \(\schStrongSelGame{\mc O_X}{\mc O_X}\) is the well-known Rothberger game,
and \(\schStrongSelGame{\mc P_X}{\neg\mc O_X}\) is isomorphic
to the point-open game \(PO(X)\): \(\plI\) chooses points of \(X\), \(\plII\) chooses an open neighborhood
of each chosen point, and \(\plI\) wins if \(\plII\)'s choices are a cover.
So this encapsulates the classic result that the Rothberger game and
point-open game are perfect-information dual \cite{MR0493925}, the more recent result that
these games are Markov-information dual \cite{CLONTZ2019106815}, and the quickly verified fact that
a Lindel\"of space \(X\) may be characterized as follows: for each neighborhood assignment (i.e.
tactic for \(\plII\) in \(PO(X)\)) there exists a countable subset
of \(X\) such that its neighborhoods cover the space.

\begin{proposition}
  \(\mc F_X\) is a reflection of \(\Omega_X\).
\end{proposition}
\begin{proof}
  For every basic open \(\omega\)-cover \(\mc U\), the corresponding choice function \(f_{\mc U}\in\mathbf C(\mc F_X)\) is simply
  the witness that for each \(\mc T_{X,F}\in\mc F_X\), there exists \(f_{\mc U}(\mc T_{X,F})\in\mc U\) such that
  \(F\subseteq f_{\mc U}(\mc T_{X,F})\).
\end{proof}

\begin{corollary}\label{coverSel2}
  \(\schStrongSelGame{\Omega_X}{\mc B}\) and \(\schStrongSelGame{\mc F_X}{\neg\mc B}\) are dual.
\end{corollary}

Note that in the case that \(\mc B=\Omega_X\), \(\schStrongSelGame{\Omega_X}{\Omega_X}\) is the Rothberger
game played with \(\omega\)-covers, and \(\schStrongSelGame{\mc F_X}{\neg\Omega_X}\) is isomorphic
to the \(\Omega\)-finite-open game \(\Omega FO(X)\): \(\plI\) chooses finite subsets of \(X\), \(\plII\) chooses an open neighborhood
of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
These games were directly shown to be Markov and perfect-information dual in \cite{CLONTZ2019106815}.

\begin{proposition}
  \(\mc T_X\) is a reflection of \(\mc D_X\).
\end{proposition}
\begin{proof}
  For every dense \(D\), the corresponding choice function \(f_D\in\mathbf C(\mc T_X)\) is simply
  the witness that for each \(U\in\mc T_X\), there exists \(f_D(U)\in U\cap D\).
\end{proof}

\begin{corollary}
  \(\schStrongSelGame{\mc D_X}{\mc B}\) and \(\schStrongSelGame{\mc T_X}{\neg\mc B}\) are perfect-information
  and Markov-information dual.
\end{corollary}

In the case that \(\mc B=\Omega_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc D_X}{\Omega_{X,x}}\) is
the strong countable dense fan-tightness game at \(x\), see e.g. \cite{MR2678950}. \(\schStrongSelGame{\mc T_X}{\neg\Omega_{X,x}}\)
is the game \(CL(X,x)\) first studied by Tkachuk in \cite{tkachukTwoPointGame}. Tkachuk showed in that paper
that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
dual in the case that \(X=C_p(Y)\)  \cite{CLONTZ2019106815}.

In the case that \(\mc B=D_X\), then \(\schStrongSelGame{\mc D_X}{\mc D_X}\) is the strong selective
separability game introduced by Scheepers 
in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
were perfect-information dual in \cite{MR1711901}.

\begin{proposition}
  \(\mc T_{X,x}\) is a reflection of \(\Omega_{X,x}\).
\end{proposition}
\begin{proof}
  For every set \(Y\) with limit point \(x\), the corresponding choice function \(f_Y\in\mathbf C(\mc T_{X,x})\) is simply
  the witness that for each \(U\in\mc T_{X,x}\), there exists \(f_Y(U)\in U\cap Y\).
\end{proof}

\begin{corollary}
  \(\schStrongSelGame{\Omega_{X,x}}{\mc B}\) and \(\schStrongSelGame{\mc T_{X,x}}{\neg\mc B}\) are dual.
\end{corollary}

In the case that \(\mc B=\Gamma_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\)
is Gruenhage's \(W\) game \cite{MR0413049}. Its dual \(\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) characterizes
the strong Fr\'echet-Urysohn property \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) at \(x\),
which now seen to be equivalent to \(\plII\notmarkwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\).
This allows us to obtain the following result.

\begin{corollary}
  \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\)
  if and only if
  \(\plI\notwin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\).
\end{corollary} 
\begin{proof}
  As shown in \cite{MR510910},
  \(\plII\notwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) (i.e. \(X\) is \(w\) in the
  terminology of that paper)
  if and only if \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\).
  The result follows as 
  \(\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) and
  \(\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) are dual.
\end{proof}

For \(\mc B=\Omega_{X,x}\), \(\schStrongSelGame{\mc T_{X,x}}{\neg\Omega_{X,x}}\) is the variant of
Gruenhage's \(W\) game for clustering. This game is now seen to be dual to the strong countable fan tightness game
\(\schStrongSelGame{\Omega_{X,x}}{\Omega_{X,x}}\) at \(x\).

We conclude by noting how Corollary \ref{mainResult}
was used by the authors of \cite{MR3991109} to
easily strengthen Propositions \ref{coverSel1} and \ref{coverSel2}
while this paper was still in preparation.

\begin{definition}
Let \(\mc Q\) be a collection of subsets of a topological space \(X\).
Then \(\mc O_{X,\mc Q}\) is the collection of basic open covers \(\mc U\) such that for
each \(Q\in\mc Q\), there is \(U\in\mc U\) with \(Q\subseteq U\).
Likewise, \(\mc N_{X,\mc Q}=\{\mc T_{X,Q}:Q\in\mc Q\}\) where each \(\mc T_{X,Q}\) collects all
basic open sets \(U\) such that \(Q\subseteq U\). 
\end{definition}

In particular, \(\mc O_{X,[X]^1}=\mc O_X\) and \(\mc O_{X,[X]^{<\omega}}=\Omega_X\).
Likewise \(\mc N_{X,[X]^1}=\mc P_X\) and \(\mc N_{X,[X]^{<\omega}}=\mc F_X\).

\begin{theorem}[\cite{MR3991109}]
  The games \(\schStrongSelGame{\mc O_{X,\mc Q}}{\mc B}\) and
  \(\schStrongSelGame{\mc N_{X,\mc Q}}{\neg\mc B}\) are dual.
\end{theorem}

\begin{proof}
  This is immediate as \(\mc N_{X,\mc Q}\) reflects \(\mc O_{X,\mc Q}\). 
  To see this, for each
  \(\mc U\in\mc O_{X,\mc Q}\), choose \(f_{\mc U}\in\mathbf C(\mc N_{X,\mc Q})\)
  satisfying that for each \(\mc T_{X,Q}\in\mc N_{X,\mc Q}\), there exists
  \(f_{\mc U}(\mc T_{X,Q})\in\mc U\) such that \(Q\subseteq f_{\mc U}(\mc T_{X,Q})\).
\end{proof}

\section{Open Questions}

Let 
\(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[\mc T_X]^{<\aleph_0})\}\). 
Such \(\gamma\)-covers are related to the convergent sequences of \(C_p(X)\) (that is,
\(\Gamma_{C_p(X),\mathbf 0}\) as defined in Definition \ref{selectionSets}),
see e.g. \cite{BUKOVSKY2019239}.

\begin{question}
  Does there exist a natural reflection for \(\Gamma_{X,x}\)
  or \(\Gamma_X\)?
\end{question} 

The game \(\schSelGame{\mc A}{\mc B}\) is defined analogously to
\(\schStrongSelGame{\mc A}{\mc B}\), except \(\plII\) may choose a finite subset each round
rather than a single set.

\begin{question}
  Do there exist any duality results for \(\schSelGame{\mc A}{\mc B}\) similar to the technique
  of reflections?
\end{question}

\section{Acknowledgements}

Thanks to Prof. Jared Holshouser for his input during the writing of these results.

\bibliographystyle{plain}
\bibliography{../../bibliography}

\end{document}
